Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2021-01-01 analysis/corpus.Rmd
Fixes in 3.1

```{r}
cran_all_funs <- sum(ALL_CRAN$funs_public) + sum(ALL_CRAN$funs_private)
cran_funs <- sum(CRAN$funs_public) + sum(CRAN$funs_private)
cran_funs_with_eval <- sum(CRAN$funs_with_eval)
cran_code <- sum(CRAN$package_code)
cran_all_code <- sum(ALL_CRAN$package_code)
cran_evals <- CRAN$evals
cran_evals_hit <- CRAN$evals_hit

overview_table(
  r("CRAN all packages", ALL_CRAN),
  r("CRAN packages", CRAN),
  r("CRAN packages ratio", ratio(CRAN, ALL_CRAN)),
  r("CRAN all code", cran_all_code),
  r("CRAN all r code", sum(ALL_CRAN$package_r_code)),
  r("CRAN all native code", sum(ALL_CRAN$package_native_code)),
  r("CRAN code", cran_code),
  r("CRAN code ratio", ratio(cran_code, cran_all_code)),
  r("CRAN all funs", cran_all_funs),
  r("CRAN funs", cran_funs),
  r("CRAN funs with eval", cran_funs_with_eval),
  r("CRAN funs with eval ratio", ratio(cran_funs_with_eval, cran_funs)),
  r("CRAN all funs with eval ratio", ratio(cran_funs_with_eval, cran_all_funs)),
  r("CRAN eval call sites", sum(cran_evals)),
  r("CRAN hit eval call sites", sum(cran_evals_hit)),
  r("CRAN hit eval call sites avg ratio", percent(mean(cran_evals_hit/cran_evals))),
  r("CRAN runnable scripts", sum(ALL_CRAN$runnable_files)),
  r("CRAN runnable code", sum(ALL_CRAN$runnable_code)),
  r("CRAN runnable code examples", sum(ALL_CRAN$runnable_code_examples)),
  r("CRAN runnable code tests", sum(ALL_CRAN$runnable_code_tests)),
  r("CRAN runnable code vignettes", sum(ALL_CRAN$runnable_code_vignettes)),
)
```

@@

```{r}
```

@@

>>>>

### Cran

```{r}
cran_all_funs <- sum(ALL_CRAN$funs_public) + sum(ALL_CRAN$funs_private)
cran_funs <- sum(CRAN$funs_public) + sum(CRAN$funs_private)
cran_funs_with_eval <- sum(CRAN$funs_with_eval)
cran_code <- sum(CRAN$package_code)
cran_all_code <- sum(ALL_CRAN$package_code)
cran_evals <- CRAN$evals
cran_evals_hit <- CRAN$evals_hit
cran_runnable_code <- sum(ALL_CRAN$runnable_code)

overview_table(
  r("CRAN available packages", 16000),#length(available.packages()[,1])),
  r("CRAN all packages", ALL_CRAN),
  r("CRAN packages", CRAN),
  r("CRAN packages ratio", ratio(CRAN, ALL_CRAN)),
  r("CRAN all code", cran_all_code),
  r("CRAN all r code", sum(ALL_CRAN$package_r_code)),
  r("CRAN all native code", sum(ALL_CRAN$package_native_code)),
  r("CRAN code", cran_code),
  r("CRAN code ratio", ratio(cran_code, cran_all_code)),
  r("CRAN all funs", cran_all_funs),
  r("CRAN funs", cran_funs),
  r("CRAN funs with eval", cran_funs_with_eval),
  r("CRAN funs with eval ratio", ratio(cran_funs_with_eval, cran_funs)),
  r("CRAN all funs with eval ratio", ratio(cran_funs_with_eval, cran_all_funs)),
  r("CRAN eval call sites", sum(cran_evals)),
  r("CRAN hit eval call sites", sum(cran_evals_hit)),
  r("CRAN hit eval call sites avg ratio", percent(mean(cran_evals_hit/cran_evals))),
  r("CRAN runnable scripts", sum(ALL_CRAN$runnable_files)),
  r("CRAN runnable code", cran_runnable_code),
  r("CRAN runnable code examples", sum(ALL_CRAN$runnable_code_examples)),
  r("CRAN runnable code tests", sum(ALL_CRAN$runnable_code_tests)),
  r("CRAN runnable code vignettes", sum(ALL_CRAN$runnable_code_vignettes)),
)
```

@@

@@

### All

```{r}
overview_table(
  r("Corpus code", kaggle_code + cran_runnable`_code)
)
```

### 2021-01-01 paper/main.tex
Fixes in 3.1

\begin{abstract}
  \noindent Most dynamic languages allow users to turn text into code
  using various functions, often named \eval, with language-dependent
  semantics. The widespread use of these reflective functions hinders
  static analysis and prevents compilers from performing
  optimizations. This paper aims to provide a better sense of why
  programmers use \eval. Understanding why \eval is used in practice
  is key to finding ways to mitigate its negative impact. We have
  reasons to believe that reflective feature usage is language and
  application domain specific; we focus on data science code written
  in R, and compare our results to previous work that analyzed web
  programming in JavaScript. Dynamic analysis of a corpus of
  \CorpusAllCodeRnd lines of libraries and end-user code confirms that
  \eval is indeed in widespread use; R's \eval is more dangerous in
  some ways, and safer in others, than what was previously reported
  for JavaScript.
  %% TODO ::: Add a sentance about summarizing why users resort to
  %% eval -- Jan
\end{abstract}

@@

\vspace{2mm}\noindent\emph{The What and How.} One significant benefit
of choosing R is that every package in the CRAN repository is curated
and comes with examples of typical usage. This gives us a large code
base that we can analyze dynamically. To observe \eval we built a
two-level monitoring infrastructure:\footnote{Our infrastructure is
open source and publicly available, our anonymized code is at {\tt
  http://url.com}, a more complete artifact will be submitted to the
artifact evaluation committee. } we can monitor R programs by
instrumentation --- this gives us access to many user-visible
properties of R programs --- but we can also monitor the
inner-workings of the R interpreter --- this allows us to capture
details not exposed at the source level. Dynamic analysis is limited,
it can only observe behaviors triggered by the particular inputs
passed to a program. Luckily, CRAN libraries come with many tests and
use-cases. The choice of corpus is crucial. Our corpus has been
constructed to reflect the levels of sophistication of the R
community. We distinguish between \emph{CRAN packages}
(\CorpusPackages curated packages that pass stringent quality checks
and are equipped with tests and sample data) and \emph{Kaggle scripts}
(\CorpusFinishedKaggle end-user written programs that performs a
particular data analysis task). It is reasonable to expect that \eval
usage differ between these datasets: the libraries represent a lively
ecosystem with new libraries added each day, while end user code is
often thrown together, run once, and never revisited.

@@

Our corpus is assembled out of two set of programs, one consisting of libraries
obtained from \emph{CRAN} (Comprehensive R Archive Network\footnote{CRAN is the
  largest repository of R code with over \CorpusAllCranRnd packages. It receives
  about 6 new package submissions a day~\cite{Ligges2017}}) and the other from
the \emph{Kaggle} data science competition website\footnote{\cf
  \url{https://kaggle.com}}. The intent here is to contrast code written by
experienced developers (CRAN) with code authored by typical end users of the
language (Kaggle). Another difference is that CRAN is a curated repository. Each
submitted package must abide to a number of well-formedness rules that are
automatically checked asserting certain quality. Most relevant for this work is
that all of the runnable code is tested and only a successfully running package
is admitted in the archive. Kaggle on the other hand is more like GitHub, anyone
can submit any code. All the code in our corpus is runnable, \ie we have scripts
that invoke the CRAN packages and the Kaggle programs have input data.

>>>>

\begin{abstract}
  \noindent Most dynamic languages allow users to turn text into code
  using various functions, often named \eval, with language-dependent
  semantics. The widespread use of these reflective functions hinders
  static analysis and prevents compilers from performing
  optimizations. This paper aims to provide a better sense of why
  programmers use \eval. Understanding why \eval is used in practice
  is key to finding ways to mitigate its negative impact. We have
  reasons to believe that reflective feature usage is language and
  application domain specific; we focus on data science code written
  in R, and compare our results to previous work that analyzed web
  programming in JavaScript. Dynamic analysis of a corpus of
  \CorpusCodeRnd lines of libraries and end-user code confirms that
  \eval is indeed in widespread use; R's \eval is more dangerous in
  some ways, and safer in others, than what was previously reported
  for JavaScript.
  %% TODO ::: Add a sentance about summarizing why users resort to
  %% eval -- Jan
\end{abstract}

@@

\vspace{2mm}\noindent\emph{The What and How.} One significant benefit
of choosing R is that every package in the CRAN repository is curated
and comes with examples of typical usage. This gives us a large code
base that we can analyze dynamically. To observe \eval we built a
two-level monitoring infrastructure:\footnote{Our infrastructure is
open source and publicly available, our anonymized code is at {\tt
  http://url.com}, a more complete artifact will be submitted to the
artifact evaluation committee. } we can monitor R programs by
instrumentation --- this gives us access to many user-visible
properties of R programs --- but we can also monitor the
inner-workings of the R interpreter --- this allows us to capture
details not exposed at the source level. Dynamic analysis is limited,
it can only observe behaviors triggered by the particular inputs
passed to a program. Luckily, CRAN libraries come with many tests and
use-cases. The choice of corpus is crucial. Our corpus has been
constructed to reflect the levels of sophistication of the R
community. We distinguish between \emph{CRAN packages}
(\CranAllPackages curated packages that pass stringent quality checks
and are equipped with tests and sample data) and \emph{Kaggle scripts}
(\KaggleUnique end-user written programs that performs a
particular data analysis task). It is reasonable to expect that \eval
usage differ between these datasets: the libraries represent a lively
ecosystem with new libraries added each day, while end user code is
often thrown together, run once, and never revisited.

@@

Our corpus is assembled out of two set of programs, one consisting of libraries
obtained from \emph{CRAN} (Comprehensive R Archive Network\footnote{CRAN is the
  largest repository of R code with almost \CranAvailablePackagesRnd packages.
  It receives about 6 new package submissions a day~\cite{Ligges2017}}) and the
other from the \emph{Kaggle} data science competition website\footnote{\cf
  \url{https://kaggle.com}}. The intent here is to contrast code written by
experienced developers (CRAN) with code authored by typical end users of the
language (Kaggle). Another difference is that CRAN is a curated repository. Each
submitted package must abide to a number of well-formedness rules that are
automatically checked asserting certain quality. Most relevant for this work is
that all of the runnable code is tested and only a successfully running package
is admitted in the archive. Kaggle on the other hand is more like GitHub, anyone
can submit any code. All the code in our corpus is runnable, \ie we have scripts
that invoke the CRAN packages and the Kaggle programs have input data.
